Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2016-05-31 Rédaction/Manuscript.tex
Cela compile !

\documentclass[preprint,3p, authoryear]{elsarticle}

\journal{Journal of International Economics}

@@

\begin{frontmatter}

\author[rvt]{Guillaume Corlay}
\author[rvt]{Stephane Dupraz\corref{cor1} \fnref{fn1}}
\author[rvt]{Claire Labonne}
\author[rvt]{Anne Muller}
\author[rvt]{Guillaume Daudin}
\cortext[cor1]{Corresponding author}
\ead{guillaume.daudin@dauphine.fr} \fntext[fn1]{Present
affiliation: Columbia University. Personal address : 535 W.
111th street, apt 64, 10025 New York NY. Phone number:
646-320-9026.}

\address[rvt]{ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff Cedex, FRANCE}

$\date{March 2, 2012}

@@

\begin{keyword}
Trade costs, globalization, gravity model, aggregation,
structure effect.
\end{keyword}

\end{frontmatter}

@@

However, Jacks, Meissner and Novy suggest in their article that
\cite{AW2003}'s model can be used to move away from the gravity
regression approach. Instead of explaining trade flows by
observable proxies for costs, they quantify the impact of all
impediments to trade: \emph{``We, therefore, infer trade costs
from trade flows. This approach allows us to capture the
combined magnitude of tariffs, transport costs, and all other
macroeconomic frictions that impede international market
integration but which are inherently difficult to observe. We
emphasize that this approach of inferring trade costs from
readily available trade data holds clear advantages for applied
research: the constraints on enumerating «--» let alone,
collecting data on «--» every individual trade cost element
even over short periods of time makes a direct accounting
approach impossible.''} (p.131).

@@

\section*{Acknowledgments}

We are grateful to Celine Antonin (OFCE) and Guillaume Daudin
(EQUIPPE (Lille I) \& OFCE) for their constant supply of
helpful comments. They, of course, bear no responsibility for
remaining errors.

@@

\nocite{*}
\bibliographystyle{elsarticle-harv}
\bibliography{bibliography}

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}  
%Langue utilisée
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\emergencystretch=8em
\usepackage[margin=1in]{geometry}

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[1]{Claire Labonne}
\author[1]{Anne Muller}
%\author[3]{Guillaume Daudin}
\author[3]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr, }\footnote{We are grateful to Celine Antonin (OFCE) for her constant supply of helpful comments. She, of course, bears no responsibility for remaining errors.}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE
Université Paris-Dauphine, PSL Research University, LEDa, UMR [225], DIAL, 75016 PARIS, FRANCE

SciencesPo, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}

%\date{March 2, 2012}

@@

\maketitle

@@

Keywords: Trade costs, globalization, gravity model, aggregation,
structure effect.
JEL Code:

@@

However, Jacks, Meissner and Novy suggest in their article that
\cite{AW2003}'s model can be used to move away from the gravity
regression approach. Instead of explaining trade flows by
observable proxies for costs, they quantify the impact of all
impediments to trade: \emph{``We, therefore, infer trade costs
from trade flows. This approach allows us to capture the
combined magnitude of tariffs, transport costs, and all other
macroeconomic frictions that impede international market
integration but which are inherently difficult to observe. We
emphasize that this approach of inferring trade costs from
readily available trade data holds clear advantages for applied
research: the constraints on enumerating — let alone,
collecting data on — every individual trade cost element
even over short periods of time makes a direct accounting
approach impossible.''} (p.131).

@@

@@

\nocite{*}
\bibliographystyle{apalike}
\bibliography{bibliography}
